Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-28 manuscript.Rmd
more introduction

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data, and each has yielded encouraging validation results. @AiraksinenRasanen2020 tested 4- to 8-month-olds in a laboratory visit, and found 95% accuracy in distinguishing between body position categories. Using a wider age range of XX-XX, [FRANCHAK] found XX% accuracy in a laboratory validation study in categorizing body position.

@@

>>>>

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data, and each has yielded encouraging validation results. @AiraksinenRasanen2020 tested 4- to 8-month-olds in a laboratory visit, and found XX% accuracy (kappa = XX%) in distinguishing between body position categories that crawling infants could perform on the floor (excluding times that infants were held by caregivers). Using a wider age range of XX-XX, [FRANCHAK] found XX% accuracy (kappa = XX%) in a laboratory validation study in categorizing body position that included infants who could both crawl and walk and also categorized caregiver holding. Most recently, [Airaksinen NEW] conducted a validation study of body position classification in either a home or clinic testing in 4- to 19-month-olds, refining their previous method to detect moments that infants were carried by caregivers. Classification accuracy did not vary between lab and home settings, and was generally high (95%, kappa = .93). However, in all three studies accuracy was assessed within a brief (15-60 minute) session supervised by a researcher, leaving the open question of how well body position classification will scale to testing across an entire day of natural home life. YAO?

@@

Accordingly, the overarching goal of the current study is to test the feasibility and validity of long-form body position recording in the home during unsupervised, everyday behavior. During a supervised recording, whether in the home or in the lab, the researcher can set up the situation to encourage or restrict certain behaviors and will usually instruct the caregiver to play with the infant. Within-day variations in activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. Will models trained on video recorded observations at the beginning of the day generalize to predict later behavior?
